### 2025-02-25 paper/intro.tex
Rewrite slightly.

   Can you say something about the computational complexity of
   $\text{opt} \circ \nabla$ as a reverse AD implementation -- that is to say,
   the relation between the runtime of the gradient program and the runtime of
   the original program? Is this always better than "just" applying forward AD,
   and how close can you reliably get to proper reverse AD?
}
\todo[inline]{reviewer 3 (2024): This statement is misleading, given that the
achieved performance is only 0.81x of the baseline. The performance ratio needs
to be reported, or at least this sentence weakened. Same in the conclusion. ---
fuck you, reviewer 3!}
The year is 2024, and we still have to make a formidable choice between
correctness and performance for all the programming projects that we start.
Low level programming languages such as C or Fortran make it possible to leverage
intricate hardware features for the price of poor analysability and
correctness guarantees.  Dependently-typed systems such as Lean or Agda make it possible
to describe arbitrary invariants within the given program, yet they can
rarely generate high-performance code.

The idealist inside of us is exasperated, because there should be a perfect
solution that caters for both cases.  However, the practitioner within us
proposes a different perspective.
Instead of using a single language, we may use two languages
in cooperation.  Specifically, we envision an alliance between a
proof assistant, from which we extract code for some high-performance language of our choice.

>>>>

   Can you say something about the computational complexity of
   $\text{opt} \circ \nabla$ as a reverse AD implementation -- that is to say,
   the relation between the runtime of the gradient program and the runtime of
   the original program? Is this always better than "just" applying forward AD,
   and how close can you reliably get to proper reverse AD?
}
\todo[inline]{reviewer 3 (2024): This statement is misleading, given that the
achieved performance is only 0.81x of the baseline. The performance ratio needs
to be reported, or at least this sentence weakened. Same in the conclusion. ---
fuck you, reviewer 3!}
\todo[inline]{mention that we are doing MNIST stuff here}
The year is 2025, and we still have to make a formidable choice between
correctness and performance for all the programming projects that we start.
Low level programming languages such as C or Fortran make it possible to leverage
intricate hardware features for the price of poor analysability and
correctness guarantees.  Dependently-typed systems such as Lean or Agda make it possible
to describe arbitrary invariants within the given program, yet they can
rarely generate high-performance code.

The idealist inside of us is exasperated, because there should be a
perfect solution that caters for both cases. However, the practitioner
within us proposes a different perspective. Instead of using a single
language, we may use two languages in cooperation. Specifically, we
envision an alliance between a proof assistant and some
high-performance language of our choice, where we extract code from
the latter to the former.
